Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-10-15 doc/JFLA2022/paper.tex
loc counts right-aligned in table
acks section not numbered
Hydras & Co. galaxy.

Both due to its prior stages~\cite{PCiota,JFLA2018paper} and the recent integrations described just above, the current \Hydras \coq code has a complex inheritance. Figure~\ref{fig:genealogy} illustrates the relationships between \Hydras packages and show their ancestry from historical Coq contributions. To indicate the scope and relative sizes of packages, Table~\ref{tbl:loc} breaks down lines of code for each \Hydras package, as reported by the \texttt{coqwc} tool, and lists their repository names in \community and identifiers in the \coq opam package index~\cite{CoqPackageIndex}.

@@

\begin{table}[ht]
\centering
\footnotesize
\begin{tabular}{llllll}
\hline
\textbf{Package name} & \textbf{Repository} & \textbf{Index identifier} & \textbf{Version} & \textbf{Spec LOC} & \textbf{Proof LOC}\\
\hline
Pocklington & \href{https://github.com/coq-community/pocklington}{\texttt{pocklington}} & \texttt{coq-pocklington} & \texttt{8.12.0} & 825 & 3,798 \\
Goedel & \href{https://github.com/coq-community/goedel}{\texttt{goedel}} & \texttt{coq-goedel} & \texttt{8.13.0} & 2,799 & 10,762 \\
Gaia & \href{https://github.com/coq-community/gaia}{\texttt{gaia}} & \texttt{coq-gaia} & \texttt{1.12} & 28,850 & 124,839 \\
Hydra-battles & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-hydra-battles} & \texttt{0.5} & & \\
Addition-chains & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-addition-chains} & \texttt{0.5} & & \\
Gaia-hydras & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-gaia-hydras} & \texttt{0.5} & & \\
\hline
\end{tabular}
\caption{Current numbers of lines of code for \Hydras packages.}
\label{tbl:loc}
\end{table}

@@

\section{Acknowledgments}
\label{sect:acks}
We are grateful to the original authors and current maintainers of the Coq packages we use and depend on: José Grimm (Gaia), Russell O'Connor (Goedel), Matthieu Sozeau (Equations), the Mathematical Components team, Marc Lasson and Chantal Keller (Paramcoq), and the authors and maintainers of \coq and its associated tools.

>>>>

Both due to its prior stages~\cite{PCiota,JFLA2018paper} and the recent integrations described just above, the current \Hydras \coq code has a complex inheritance. Figure~\ref{fig:genealogy} illustrates the relationships between \Hydras packages and show their ancestry from historical Coq contributions. To indicate the scope and relative sizes of packages, Table~\ref{tbl:loc} breaks down lines of code for each package in the \Hydras galaxy, as reported by the \texttt{coqwc} tool, and lists their repository names in \community and identifiers in the \coq opam package index~\cite{CoqPackageIndex}.

@@

\begin{table}[ht]
\centering
\footnotesize
\begin{tabular}{llllrr}
\hline
\textbf{Package name} & \textbf{Repository} & \textbf{Index identifier} & \textbf{Version} & \textbf{Spec LOC} & \textbf{Proof LOC}\\
\hline
Pocklington & \href{https://github.com/coq-community/pocklington}{\texttt{pocklington}} & \texttt{coq-pocklington} & \texttt{8.12.0} & 825 & 3,798 \\
Goedel & \href{https://github.com/coq-community/goedel}{\texttt{goedel}} & \texttt{coq-goedel} & \texttt{8.13.0} & 2,799 & 10,762 \\
Gaia & \href{https://github.com/coq-community/gaia}{\texttt{gaia}} & \texttt{coq-gaia} & \texttt{1.12} & 28,850 & 124,839 \\
Hydra-battles & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-hydra-battles} & \texttt{0.5} & 14,368 & 48,385 \\
Addition-chains & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-addition-chains} & \texttt{0.5} & 1,961 & 2,210 \\
Gaia-hydras & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-gaia-hydras} & \texttt{0.5} & 81 & 177 \\
\hline
\end{tabular}
\caption{Current numbers of lines of code for packages in the \Hydras galaxy.}
\label{tbl:loc}
\end{table}

@@

\section*{Acknowledgments}
\label{sect:acks}
We are grateful to the original authors and current maintainers of the Coq packages we use and depend on: José Grimm (Gaia), Russell O'Connor (Goedel), Matthieu Sozeau (Equations), the Mathematical Components team, Marc Lasson and Chantal Keller (Paramcoq), and the authors and maintainers of \coq and its associated tools.
